Jean Pockets and Gender\thanks{Code and data are available at: https://github.com/hari-lr/pockets-and-gender}

### 2024-04-24 paper/paper.tex
update

\begin{document}
\maketitle
\begin{abstract}
Fashion has long reflected and reinforced gender inequalities, with
women's clothing often lacking functional pockets found in men's
garments. A 2018 study by Jan Diehm \& Amber Thomas on The Pudding
revealed this discrepancy, highlighting inferior pocket functionality in
women's jeans. This paper aims to reproduce these findings and explore
if gender disparities extend to pricing. Using the same data, we analyze
the correlation between prices of men's and women's jeans. Results
suggest that women's jeans not only have smaller pockets but also tend
to be more expensive. This study sheds light on gender inequalities in
everyday products and their broader implications. {[}UPDATE according to
findingsThe findings revealed that pocket area alone may not be a strong
predictor of jeans prices for either gender, and there may be other
factors influencing the pricing of jeans.{]}
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, interior hidden, sharp corners, breakable]}{\end{tcolorbox}}\fi

>>>>

\begin{document}
\maketitle
\begin{abstract}
Fashion has long reflected and reinforced gender inequalities, with
women's clothing often lacking functional pockets found in men's
garments. A 2018 study by Jan Diehm \& Amber Thomas on The Pudding
revealed this discrepancy, highlighting inferior pocket functionality in
women's jeans. This paper aims to reproduce these findings and explore
if gender disparities extend to pricing. Using the same data, we analyze
the correlation between prices of men's and women's jeans. Results
suggest that women's jeans not only have smaller pockets but also tend
to be more expensive. This study sheds light on gender inequalities in
everyday products and their broader implications. {[}UPDATE according to
findingsThe findings revealed that pocket area alone may not be a strong
predictor of jeans prices for either gender, and there may be other
factors influencing the pricing of jeans.{]}
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, borderline west={3pt}{0pt}{shadecolor}, interior hidden, frame hidden, enhanced, boxrule=0pt, breakable]}{\end{tcolorbox}}\fi
